Dismal Code: Studying the Evolution of Security Vulnerabilities

### 2013-02-04 docs/msr.tex
some chenges in the data provenance section. Additions in the introduction

A security bug is a programming error that introduces a potentially
exploitable weakness into a computer system~\cite{SSL12}. This weakness could lead to a
security breach with unfortunate consequences in different layers, like databases,
native code, applications, libraries and others. Despite the significant
effort to detect and eliminate such bugs~\cite{SZ12}, little attention has been paid to
study them in relation to software evolution~\cite{L96, LRWPT97, IB06}. In this paper we present how we
used a large software ecosystem to analyze how evolving software packages are
related to the different types of security vulnerabilities.

@@

We chose to focus our study on the security bugs rather than other
software bugs. This is because compared to other bug categories,
the category of security bugs has a distinct feature: it is critical. Specifically, a software bug can
lead to a mulfunction of a software artifact that runs under specific
requirements but a security bug can allow a malicious user to alter the
execution of the entire application. In this case, such bugs could span a wide range
of security and privacy issues, like viewing sensitive information, the destruction or
modification of sensitive data, denial of service and others.
Hence, one of the basic pursuits in every new software release should be the
mitigation of such bugs.

@@

The subject of our study was a snapshot of the maven repository. Before
analyzing the data of the repository we performed a number of functional fits
on the data.

Initially, we obtained a snapshot (January 2012) of the maven repository and
handled it locally to retreive a list of all the names of the project versions that existed in the
repository. Our first problem was that Maven repository hosts projects from languages other than Java, typically languages that produce executable code for the {\sc jvm} (Java Virtual Machine), such as Scala, Groovy, Clojure etc. These projects were filtered out by a series of filter and checks in the repository data and metadata.

In addition, we implemented a series of checks in the \textit{worker} scripts that checked if the jars are valid in terms of language implementation. After the project filtering we narrowed down our data set to 17,055 projects with 114,399 versions. Table \ref{tbl:repository} summarises the data set information and in addition provides the basic descriptive statistic measurements. The distribution of version count among the selected projects is presented in Figure \ref{fig:version-count}.

@@

It was quite expected that the repository has many project with a few number of versions, than many projects with many versions each. The statistical mesurements presented in Table \ref{tbl:repository} indicate that we have 17,505 projects total and the data sets median is 3, which means that almost 50\% (8,753 projects) of the project population has 1 to 3 versions. There are a few projects with tens of versions and only a few with hundreds. The maximum number of versions for a project is 337. The 3$^{rd}$ quartile measurement also indicated that 75\% (13,129) of the projects have a maximum of 8 versions.

>>>>

A security bug is a programming error that introduces a potentially
exploitable weakness into a computer system~\cite{SSL12, TJBD11}. This weakness could lead to a
security breach with unfortunate consequences in different layers, like databases,
native code, applications, libraries and others. Despite the significant
effort to detect and eliminate such bugs~\cite{SZ12}, little attention has been paid to
study them in relation to software evolution~\cite{L96, LRWPT97, IB06, RGMA06}.
In this paper we present how we used a large software ecosystem to analyze
how evolving software packages are related to the different types of security
vulnerabilities.

@@

We chose to focus our study on the security bugs rather than other
software bugs. This is because compared to other bug categories,
the category of security bugs has two distinct features: it is critical~\cite{SZ12}
and it costs~\cite{BCL08}. Specifically, a software bug can
lead to a mulfunction of a software artifact that runs under specific
requirements but a security bug can allow a malicious user to alter the execution
of the entire application. In this case, such bugs could span a wide
range of security and privacy issues, like viewing sensitive information, the destruction or
modification of sensitive data, denial of service and others.
Moreover, security bug disclosures lead to a negative and significant change
in market value for a software vendor~\cite{TW07}.
Hence, one of the basic pursuits in every new software release should
be the mitigation of such bugs.

@@

The subject of our study was the Maven repository. Before
analyzing the data of the repository we performed a
number of functional fits on the data.

Initially, we obtained a snapshot (January 2012) of the maven repository and
handled it locally to retreive a list of all the names of the project versions
that existed in it. Our first problem was that the Maven repository
hosts projects from languages other than Java, typically languages that produce
executable code for the {\sc jvm} (Java Virtual Machine), such as Scala, Groovy,
Clojure etc. These projects were filtered out by a series of checks in
the repository data and metadata.

In addition, we implemented a series of checks in the worker scripts that
checked if the {\sc jar}s are valid in terms of implementation. For instance,
for every {\sc jar} the worker checked if there were any {\it .class} files
before invoking FindBugs. After the project filtering we narrowed down
our data set to 17,055 projects with 114,399 versions.
Table \ref{tbl:repository} summarises the data set information and
provides the basic descriptive statistic measurements. The distribution of version
count among the selected projects is presented in Figure \ref{fig:version-count}.

@@

The repository has many project with a
few number of versions. On the contrary, there are numerous projects with a
number of versions that is less than ten.
The statistical mesurements presented in Table \ref{tbl:repository}
indicate that we have 17,505 projects total and the data sets median
is 3, which means that almost 50\% (8,753 projects) of the project
population has 1 to 3 versions. There are a few projects containing ten
versions and only a few with hundreds of versions. The maximum number of
versions for a project is 337. The 3$^{rd}$ quartile measurement
also indicated that 75\% (13,129) of the projects have a maximum of 8 versions.
